Psychological Needs During Intergroup Contact

### 2021-11-08 Methods-and-Results.Rmd
confint set to "Wald"for fixed effects for quicker renders

# generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
#                  method="boot",nsim=1000,
#                  parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-Null-CI.csv")

@@

mdlWorker$lmerInterceptAttTypeCI <- confint(mdlWorker$lmerInterceptAttType)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlWorkerOut$Att$lmerInterceptCoreCI <- 
  confint(mdlWorkerOut$Att$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

# 95%CIs
mdlWorkerOut$Att$lmerSlopesCoreCI <- confint(mdlWorkerOut$Att$lmerSlopesCore)

@@

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

# generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction),
#                  method="boot",nsim=1000,
#                  parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-Null-CI.csv")

@@

mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
  confint(mdlWorkerOut$Qlt$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
  confint(mdlWorkerOut$Qlt$lmerSlopesCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(mdlWorkerOut$Qlt$lmerSlopesCore,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
  confint(mdlWorkerOut$Att$lmerInterceptCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
  confint(mdlWorkerOut$Att$lmerSlopesCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlWorker$lmerInterceptAttCoreIntCI <- 
  confint(mdlWorker$lmerInterceptAttCoreInt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlWorker$lmerSlopesAttCoreIntCI <- 
  confint(mdlWorker$lmerSlopesAttCoreInt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
  confint(mdlWorkerOut$Att$lmerSlopesCoreSdt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

# generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
#                  method="boot",nsim=1000,
#                  parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-Null-CI.csv")

@@

mdlStudent$lmerInterceptAttTypeCI <- confint(mdlStudent$lmerInterceptAttType)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlStudent$lmerSlopesAttTypeCI <- confint(mdlStudent$lmerSlopesAttType)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlStudentOut$Att$lmerInterceptCoreCI <- 
  confint(mdlStudentOut$Att$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

# 95%CIs
mdlStudentOut$Att$lmerSlopesCoreCI <- confint(mdlStudentOut$Att$lmerSlopesCore)

@@

# generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000,
#                  parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-Null-CI.csv")

@@

mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
  confint(mdlStudentOut$Qlt$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
  confint(mdlStudentOut$Qlt$lmerSlopesCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
  confint(mdlStudentOut$Att$lmerInterceptCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
  confint(mdlStudentOut$Att$lmerSlopesCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlStudent$lmerInterceptAttCoreIntCI <- 
  confint(mdlStudent$lmerInterceptAttCoreInt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtStudent$full),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlStudent$lmerSlopesAttCoreIntCI <- 
  confint(mdlStudent$lmerSlopesAttCoreInt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
  confint(mdlStudentOut$Att$lmerSlopesCoreSdt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlMedical$lmerInterceptAttTypeCI <- confint(mdlMedical$lmerInterceptAttType)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedical$lmerSlopesAttTypeCI <- confint(mdlMedical$lmerSlopesAttType)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlMedicalOut$Att$lmerInterceptAllportCI <- 
  confint(mdlMedicalOut$Att$lmerInterceptAllport)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

# 95%CIs
mdlMedicalOut$Att$lmerSlopesAllportCI <- confint(mdlMedicalOut$Att$lmerSlopesAllport)

@@

# generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000,
#                  parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-Null-CI.csv")

@@

mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
  confint(mdlMedicalOut$Qlt$lmerInterceptAllport)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(qualityOverall ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
  confint(mdlMedicalOut$Qlt$lmerSlopesAllport)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(mdlMedicalOut$Qlt$lmerSlopesAllport,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
  confint(mdlMedicalOut$Att$lmerInterceptAllportQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedicalOut$Att$lmerSlopesAllportQltCI <- 
  confint(mdlMedicalOut$Att$lmerSlopesAllportQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

<!-- ```{r medicalOutModelMLAttNull, include=FALSE} -->
<!-- # Create and save Model -->
<!-- mdlMedicalOut$Att$lmerNull <- -->
<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
<!-- mdlMedicalOut$Att$lmeNull <- -->
<!--   lme( -->
<!--     AttitudesDutch ~ 1, -->
<!--     random = ~ 1 | PID, -->
<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
<!--     na.action = na.omit, -->
<!--     control = list(opt = "nlmimb") -->
<!--   ) # use optim if it does not converge -->

<!-- # Get summary with p-values (Satterthwaite's method) -->
<!-- # summary(Null.Out.ML.r) #or with the lme function -->
<!-- summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE) -->

<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full), -->
<!-- #                  method="boot",nsim=1000, -->
<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
<!-- #          "output/tables/ML-Null-CI.csv") -->

<!-- # Save variances -->
<!-- mdlMedicalOut$Att$varNull <-  -->
<!--   VarCorr(mdlMedicalOut$Att$lmeNull) # save variances -->
<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
<!-- mdlMedicalOut$Att$tauNull <-  -->
<!--   as.numeric(mdlMedicalOut$Att$varNull[1]) -->
<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
<!-- mdlMedicalOut$Att$sigmaNull <-  -->
<!--   as.numeric(mdlMedicalOut$Att$varNull[2]) -->
<!-- # The ICC estimate (between/between+within) is: -->
<!-- mdlMedicalOut$Att$IccNull <- -->
<!--   (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2]))) -->
<!-- mdlMedicalOut$Att$IccPercNull <- -->
<!--   ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100 -->
<!-- ``` -->
```{r medicalOutModelInterceptAttCore, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

mdlMedicalOut$Att$lmerInterceptCoreCI <-
  confint(mdlMedicalOut$Att$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

# 95%CIs
mdlMedicalOut$Att$lmerSlopesCoreCI <- confint(mdlMedicalOut$Att$lmerSlopesCore)

@@

<!-- ```{r medicalOutModelMLQltNull, include=FALSE} -->
<!-- # Create and save Model -->
<!-- mdlMedicalOut$Qlt$lmerNull <- -->
<!--   lme4::lmer(qualityOverall ~ 1 + (1 | PID),  -->
<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
<!-- mdlMedicalOut$Qlt$lmeNull <- -->
<!--   mdlMedicalOut$Qlt$lmeNull <-lme( -->
<!--     qualityOverall ~ 1, -->
<!--     random = ~ 1 | PID, -->
<!--     na.action = na.omit, -->
<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
<!--     control = list(opt = "nlmimb") -->
<!--   ) # use optim if it does not converge -->

<!-- # Get summary with p-values (Satterthwaite's method) -->
<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
<!-- summ(mdlMedicalOut$Qlt$lmerNull, digits = 3) -->

<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction), -->
<!-- #                  method="boot",nsim=1000, -->
<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
<!-- #          "output/tables/ML-Null-CI.csv") -->

<!-- # Save variances -->
<!-- mdlMedicalOut$Qlt$varNull <-  -->
<!--   VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances -->
<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
<!-- mdlMedicalOut$Qlt$tauNull <-  -->
<!--   as.numeric(mdlMedicalOut$Qlt$varNull[1]) -->
<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
<!-- mdlMedicalOut$Qlt$sigmaNull <-  -->
<!--   as.numeric(mdlMedicalOut$Qlt$varNull[2]) -->
<!-- # The ICC estimate (between/between+within) is: -->
<!-- mdlMedicalOut$Qlt$IccNull <- -->
<!--   (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2]))) -->
<!-- mdlMedicalOut$Qlt$IccPercNull <- -->
<!--   ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100 -->
<!-- ``` -->

@@

mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
  confint(mdlMedicalOut$Qlt$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(qualityOverall ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
  confint(mdlMedicalOut$Qlt$lmerSlopesCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(mdlMedicalOut$Qlt$lmerSlopesCore,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
  confint(mdlMedicalOut$Att$lmerInterceptCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
  confint(mdlMedicalOut$Att$lmerSlopesCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
  confint(mdlMedicalOut$Att$lmerInterceptCoreAllport)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
  confint(mdlMedicalOut$Att$lmerSlopesCoreAllport, method = "Wald")

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

mdlMedical$lmerInterceptAttCoreIntCI <- 
  confint(mdlMedical$lmerInterceptAttCoreInt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtMedical$full),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedical$lmerSlopesAttCoreIntCI <- 
  confint(mdlMedical$lmerSlopesAttCoreInt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

@@

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

@@

mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
  confint(mdlMedicalOut$Att$lmerSlopesCoreSdt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(model.ran0,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

>>>>

@@

mdlWorker$lmerInterceptAttTypeCI <- 
  confint(method = "Wald", mdlWorker$lmerInterceptAttType)

@@

mdlWorkerOut$Att$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCore)

@@

# 95%CIs
mdlWorkerOut$Att$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCore)

@@

@@

@@

mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Qlt$lmerInterceptCore)

@@

mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Qlt$lmerSlopesCore)

@@

mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreQlt)

@@

mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreQlt)

@@

mdlWorker$lmerInterceptAttCoreIntCI <- 
  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)

@@

mdlWorker$lmerSlopesAttCoreIntCI <- 
  confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt)

@@

@@

mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt)

@@

@@

mdlStudent$lmerInterceptAttTypeCI <- 
  confint(method = "Wald", mdlStudent$lmerInterceptAttType)

@@

mdlStudent$lmerSlopesAttTypeCI <- 
  confint(method = "Wald", mdlStudent$lmerSlopesAttType)

@@

mdlStudentOut$Att$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCore)

@@

# 95%CIs
mdlStudentOut$Att$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCore)

@@

@@

mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlStudentOut$Qlt$lmerInterceptCore)

@@

mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlStudentOut$Qlt$lmerSlopesCore)

@@

mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreQlt)

@@

mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreQlt)

@@

mdlStudent$lmerInterceptAttCoreIntCI <- 
  confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt)

@@

mdlStudent$lmerSlopesAttCoreIntCI <- 
  confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt)

@@

@@

mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt)

@@

mdlMedical$lmerInterceptAttTypeCI <- 
  confint(method = "Wald", mdlMedical$lmerInterceptAttType)

@@

mdlMedical$lmerSlopesAttTypeCI <- 
  confint(method = "Wald", mdlMedical$lmerSlopesAttType)

@@

mdlMedicalOut$Att$lmerInterceptAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)

@@

# 95%CIs
mdlMedicalOut$Att$lmerSlopesAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)

@@

@@

mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptAllport)

@@

mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesAllport)

@@

mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllportQlt)

@@

mdlMedicalOut$Att$lmerSlopesAllportQltCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllportQlt)

@@

```{r medicalOutModelInterceptAttCore, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

mdlMedicalOut$Att$lmerInterceptCoreCI <-
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCore)

@@

# 95%CIs
mdlMedicalOut$Att$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCore)

@@

@@

mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptCore)

@@

mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesCore)

@@

mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreQlt)

@@

mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreQlt)

@@

mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreAllport)

@@

mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreAllport)

@@

mdlMedical$lmerInterceptAttCoreIntCI <- 
  confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt)

@@

mdlMedical$lmerSlopesAttCoreIntCI <- 
  confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt)

@@

@@

mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt)
